Analysis of Cartesian Genetic Programming's Evolutionary Mechanisms

### 2013-07-23 CGP Journal/main.tex
Added stuff for Bill's bio

% if you will not have a photo at all:
\begin{IEEEbiography}{William F. Punch}
TODO
\end{IEEEbiography}

>>>>

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{headPunch}}]{William F. Punch}
Bill Punch received his Ph.D. from the Ohio State University and is currently an
Associate Professor at the Computer Science and Engineering Department of Michigan
State University. He is also the  director of the MSU High Performance Computing
Center. His research interests are evolutionary computation, high performance
computing and computing pedagogy. He co-directs the Genetic Algorithms Research
and Application Group (GARAGe) and is on the executive committee of the NSF STC,
BEACON, at MSU. His book with Rich Enbody titled "The Practice of Computing Using
Python" is now in its second edition.
\end{IEEEbiography}
